Research Journal

### 2018-07-05 journal/main.tex

>>>>

\subsection*{TensorFlow Implementation Details}
So my TensorFlow code is OK but it lacks some nice features.
Talking to Drew, it seems Sonnet is the answer, since he showed me some of the features I was missing.
I also need to start using \texttt{SingularMonitoredSession} instead of slim since slim is just... annoying.
So I will need to branch off in git and make a new branch while I get Sonnet working.
